---
title: "Analysis Loneliness"
author: "Jesus Sierralaya"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(rmarkdown)
library(labelled)
library(gtsummary)
library(tidyverse)
library(lme4)
library(kableExtra)
library(survey)
library(haven)
library(gt)
library(sjPlot)
```

## Format long 2 (without NA)

For the mixed model.

```{r}
load(
  here("dat","db_longer.Rda")
)

# # Values and Variable Labels 
# db_longer |> look_for(details = "full")
# 
# paged_table(db_longer, options = list(rows.print = 6))
```

## Format wide

To apply the weights and the estimation of the models. 

```{r}
load(
  here("dat","db_pre_post.Rda")
)

# # Values and Variable Labels 
# db_pre_post |> look_for(details = "full")
# 
# paged_table(db_pre_post, options = list(rows.print = 6))
```

<!-- # Comparison of means -->

<!-- Compare levels between the Age_cat and Assessment (pre-post) -->

<!-- ```{r message=FALSE, warning=FALSE} -->
<!-- db_longer |> group_by(q1011_age_cat, Assessment) |>  -->
<!--   dplyr::summarise(across(Loneliness, lst(mean, sd), na.rm = TRUE)) |>  -->
<!--   kableExtra::kable()|>  -->
<!--   kable_styling(full_width = FALSE) -->
<!-- ``` -->

<!-- # Fit Test for Age cat -->

<!-- ```{r message=FALSE, warning=FALSE} -->
<!-- # Age model test -->
<!-- Fit_age_test <- lmer(Loneliness ~ 0 + q1011_age_cat * Assessment + (1 | ID_ECS),  -->
<!--              data = db_longer) -->
<!-- # Anova -->
<!-- anova(Fit_age_test) |>  -->
<!--   round(2) |> gt() -->

<!-- summary(Fit_age_test)$coefficients |> round(3)  -->

<!-- # tbl regression -->
<!-- Fit_age_test |> tbl_regression( -->
<!--     estimate_fun = function(x) style_ratio(x, digits = 3) -->
<!-- ) |> add_global_p() |> add_vif() -->
<!-- ``` -->

# Univariates

## Pre-process

```{r}
# Select the reference group
db_pre_post <- db_pre_post |> 
  mutate(
      q1011_age_cat = q1011_age_cat |> fct_relevel("50-64"),
      q1012_mar_stat_recat = q1012_mar_stat_recat |> to_factor() |> 
        fct_relevel("Married/ Partnership"),
      q1016_highest_recat = q1016_highest_recat |> to_factor() |> fct_relevel("Tertiary"),
      SOLO3 = SOLO3 |> to_factor() |> fct_relevel("Have had no effect"),
  )
# As factor
db_pre_post <- db_pre_post |> 
  haven::as_factor()
```

## Survey design

```{r message=FALSE, warning=FALSE}
svy_design <- svydesign(
  data = db_pre_post,
  ids = ~ID_ECS,
  weights = db_pre_post$wfinal_norm
)
```

## Null model

Model to compare with univariates

```{r}
fit_null <-  svyglm(loneliness_post ~ offset(loneliness_pre),
             design  = svy_design)
fit_null$coefficients
```

## Univariates

```{r}
# Sex 
fit_sex <-  
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre) 
    + q1009_sex,
    design  = svy_design
  )

# Coefficients -------
fit_sex |> tbl_regression(intercept = TRUE)
# --------------------

# anova tests the models against one another
# Tests whether there are statistically significant differences 
# Is there a difference in the population between the different models?

anova_sex <- anova(fit_sex, fit_null)

select_covs <- c(q1009_sex = anova_sex$p < .05)

# Age

fit_age <-  
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre) 
    + q1011_age,
    design  = svy_design
  )

# Coefficients -------
fit_age |> tbl_regression(intercept = TRUE)
# --------------------

anova_age <- anova(fit_age, fit_null)

select_covs <- select_covs |> c(q1011_age = anova_age$p < .05)

# Age cat

fit_age_cat <-  
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre) 
    + q1011_age_cat,
    design  = svy_design
  )

# Coefficients -------
fit_age_cat |> tbl_regression(intercept = TRUE)
# --------------------

anova_age_cat <- anova(fit_age_cat, fit_null)

select_covs <- select_covs |> c(q1011_age_cat = anova_age_cat$p < .05)

# Marital status

fit_mar_stat <-  
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre) 
    + q1012_mar_stat_recat,
    design  = svy_design
  )

# Coefficients -------
fit_mar_stat |> tbl_regression(intercept = TRUE)
# --------------------

anova_mar_stat <- anova(fit_mar_stat, fit_null)

select_covs <- select_covs |> c(q1012_mar_stat_recat = anova_mar_stat$p < .05)

# Education level

fit_ed_level <-  
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre) 
    + q1016_highest_recat,
    design  = svy_design
  )

# Coefficients -------
fit_ed_level |> tbl_regression(intercept = TRUE)
# --------------------

anova_ed_level <- anova(fit_ed_level, fit_null)

select_covs <- select_covs |> c(q1016_highest_recat = anova_ed_level$p < .05)

# Social relationship

fit_SOLO3 <-  
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre) 
    + SOLO3,
    design  = svy_design
  )

# Coefficients -------
fit_SOLO3 |> tbl_regression(intercept = TRUE)
# --------------------
anova_SOLO3 <- anova(fit_SOLO3, fit_null)

select_covs <- select_covs |> c(SOLO3 = anova_SOLO3$p < .05)

# Economy post

fit_econ_post <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + economy_post,
    design  = svy_design
  )

# Coefficients -------
fit_econ_post |> tbl_regression(intercept = TRUE)
# --------------------

anova_econ_post <- anova(fit_econ_post, fit_null)

select_covs <- select_covs |> c(economy_post = anova_econ_post$p < .05)

# resilience scale post

fit_resilience_post <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + resilience_scale_post,
    design  = svy_design
  )

# Coefficients -------
fit_resilience_post |> tbl_regression(intercept = TRUE)
# --------------------

anova_resilience_post <- anova(fit_resilience_post, fit_null)

select_covs <- select_covs |> c(resilience_scale_post = anova_resilience_post$p < .05)

# Living alone post

fit_living_alone_post <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + living_alone_post,
    design  = svy_design
  )

# Coefficients -------
fit_living_alone_post |> tbl_regression(intercept = TRUE)
# --------------------

anova_living_alone_post <- anova(fit_living_alone_post, fit_null)

select_covs <- select_covs |> c(living_alone_post = anova_living_alone_post$p < .05)

# neuroticism

fit_neuroticism <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + neuroticism,
    design  = svy_design
  )

# Coefficients -------
fit_neuroticism |> tbl_regression(intercept = TRUE)
# --------------------

anova_neuroticism <- anova(fit_neuroticism, fit_null)

select_covs <- select_covs |> c(neuroticism = anova_neuroticism$p < .05)

# extraversion

fit_extraversion <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + extraversion,
    design  = svy_design
  )

# Coefficients -------
fit_extraversion |> tbl_regression(intercept = TRUE)
# --------------------

anova_extraversion <- anova(fit_extraversion, fit_null)

select_covs <- select_covs |> c(extraversion = anova_extraversion$p < .05)

# physical post

fit_physical_post <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + physical_post,
    design  = svy_design
  )

# Coefficients -------
fit_physical_post |> tbl_regression(intercept = TRUE)
# --------------------

anova_physical_post <- anova(fit_physical_post, fit_null)

select_covs <- select_covs |> c(physical_post = anova_physical_post$p < .05)

# # Anxiety pre
# 
# fit_GAD12m_pre <-
#   svyglm(
#     formula = loneliness_post ~ offset(loneliness_pre)
#     + GAD12m_pre,
#     design  = svy_design
#   )
# 
# # Coefficients -------
# fit_GAD12m_pre |> tbl_regression(intercept = TRUE)
# # --------------------
# 
# anova_GAD12m_pre <- anova(fit_GAD12m_pre, fit_null)
# 
# select_covs <- select_covs |> c(GAD12m_pre = anova_GAD12m_pre$p < .05)

# Panic pre

fit_PAN12m_pre <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + PAN12m_pre,
    design  = svy_design
  )

# Coefficients -------
fit_PAN12m_pre |> tbl_regression(intercept = TRUE)
# --------------------

anova_PAN12m_pre <- anova(fit_PAN12m_pre, fit_null)

select_covs <- select_covs |> c(PAN12m_pre = anova_PAN12m_pre$p < .05)

# whodas 12 pre

fit_whodas12_pre <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + whodas12_pre,
    design  = svy_design
  )

# Coefficients -------
fit_whodas12_pre |> tbl_regression(intercept = TRUE)
# --------------------

anova_whodas12_pre <- anova(fit_whodas12_pre, fit_null)

select_covs <- select_covs |> c(whodas12_pre = anova_whodas12_pre$p < .05)

# whodas 12 post

fit_whodas12_post <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + whodas12_post,
    design  = svy_design
  )

# Coefficients -------
fit_whodas12_post |> tbl_regression(intercept = TRUE)
# --------------------

anova_whodas12_post <- anova(fit_whodas12_post, fit_null)

select_covs <- select_covs |> c(whodas12_post = anova_whodas12_post$p < .05)

# social support pre

fit_social_support_pre <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + social_support_pre_original,
    design  = svy_design
  )

# Coefficients -------
fit_social_support_pre |> tbl_regression(intercept = TRUE)
# --------------------

anova_social_support_pre <- anova(fit_social_support_pre, fit_null)

select_covs <- select_covs |> c(social_support_pre = anova_social_support_pre$p < .05)

# social support post

fit_social_support_post <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + social_support_post_original,
    design  = svy_design
  )

# Coefficients -------
fit_social_support_post |> tbl_regression(intercept = TRUE)
# --------------------

anova_social_support_post <- anova(fit_social_support_post, fit_null)

select_covs <- select_covs |> c(social_support_post = anova_social_support_post$p < .05)

# depression pre

fit_depression_pre <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + depression_12m_pre,
    design  = svy_design
  )

# Coefficients -------
fit_depression_pre |> tbl_regression(intercept = TRUE)
# --------------------

anova_depression_pre <- anova(fit_depression_pre, fit_null)

select_covs <- select_covs |> c(depression_12m_pre = anova_depression_pre$p < .05)

# depression post

fit_depression_post <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    + depression_30d_post,
    design  = svy_design
  )

# Coefficients -------
fit_depression_post |> tbl_regression(intercept = TRUE)
# --------------------

anova_depression_post <- anova(fit_depression_post, fit_null)

select_covs <- select_covs |> c(depression_30d_post = anova_depression_post$p < .05)

# p < 0.05
select_covs

cov_sig <- which(select_covs == TRUE)

names(cov_sig)
```

## Forestplot univariates

```{r, fig.width=7 , fig.height= 10}
# SEX
beta_sex <- coefficients(fit_sex)["q1009_sexFemale"]
lower_sex <- confint(fit_sex)["q1009_sexFemale","2.5 %"]
upper_sex <- confint(fit_sex)["q1009_sexFemale","97.5 %"]

# AGE - Ref: Male
beta_age <- coefficients(fit_age)["q1011_age"]
lower_age <- confint(fit_age)["q1011_age","2.5 %"]
upper_age <- confint(fit_age)["q1011_age","97.5 %"]

# Age cat - Ref: 50-64
# AGE GROUPED 18-34	
beta_age_cat_18_34 <- coefficients(fit_age_cat)["q1011_age_cat18-34"]
lower_age_cat_18_34 <- confint(fit_age_cat)["q1011_age_cat18-34","2.5 %"]
upper_age_cat_18_34 <- confint(fit_age_cat)["q1011_age_cat18-34","97.5 %"]
# AGE GROUPED 35-49	
beta_age_cat_35_49 <- coefficients(fit_age_cat)["q1011_age_cat35-49"]
lower_age_cat_35_49 <- confint(fit_age_cat)["q1011_age_cat35-49","2.5 %"]
upper_age_cat_35_49 <- confint(fit_age_cat)["q1011_age_cat35-49","97.5 %"]
# AGE GROUPED >65 	
beta_age_cat_65 <- coefficients(fit_age_cat)["q1011_age_cat+65"]
lower_age_cat_65 <- confint(fit_age_cat)["q1011_age_cat+65","2.5 %"]
upper_age_cat_65 <- confint(fit_age_cat)["q1011_age_cat+65","97.5 %"]

# Marital status - ref: Married/ partnership
# Marital status single
beta_mar_stat_single <- coefficients(fit_mar_stat)["q1012_mar_stat_recatSingle"]
lower_mar_stat_single <- confint(fit_mar_stat)["q1012_mar_stat_recatSingle","2.5 %"]
upper_mar_stat_single <- confint(fit_mar_stat)["q1012_mar_stat_recatSingle","97.5 %"]
# Marital status Separated/ Widowed 
beta_mar_stat_sep_wid<- coefficients(fit_mar_stat)["q1012_mar_stat_recatSeparated/ Widowed"]
lower_mar_stat_sep_wid <- confint(fit_mar_stat)["q1012_mar_stat_recatSeparated/ Widowed","2.5 %"]
upper_mar_stat_sep_wid <- confint(fit_mar_stat)["q1012_mar_stat_recatSeparated/ Widowed","97.5 %"]

# Education level - Ref: Tertiary
# Education level Less than primary	
beta_ed_level_less_prim <- coefficients(fit_ed_level)["q1016_highest_recatLess than primary"]
lower_ed_level_less_prim <- confint(fit_ed_level)["q1016_highest_recatLess than primary","2.5 %"]
upper_ed_level_less_prim <- confint(fit_ed_level)["q1016_highest_recatLess than primary","97.5 %"]
# Education level Primary	
beta_ed_level_prim <- coefficients(fit_ed_level)["q1016_highest_recatPrimary"]
lower_ed_level_prim <- confint(fit_ed_level)["q1016_highest_recatPrimary","2.5 %"]
upper_ed_level_prim <- confint(fit_ed_level)["q1016_highest_recatPrimary","97.5 %"]
# Education level Secondary	
beta_ed_level_sec <- coefficients(fit_ed_level)["q1016_highest_recatSecondary"]
lower_ed_level_sec <- confint(fit_ed_level)["q1016_highest_recatSecondary","2.5 %"]
upper_ed_level_sec <- confint(fit_ed_level)["q1016_highest_recatSecondary","97.5 %"]

# Social relat - Have had no effects
# Social relationships changes - Have improved	
beta_solo3_impr <- coefficients(fit_SOLO3)["SOLO3Have improved"]
lower_solo3_impr <- confint(fit_SOLO3)["SOLO3Have improved","2.5 %"]
upper_solo3_impr <- confint(fit_SOLO3)["SOLO3Have improved","97.5 %"]
# Social relationships changes - Have worsened	
beta_solo3_wors <- coefficients(fit_SOLO3)["SOLO3Have worsened"]
lower_solo3_wors <- confint(fit_SOLO3)["SOLO3Have worsened","2.5 %"]
upper_solo3_wors <- confint(fit_SOLO3)["SOLO3Have worsened","97.5 %"]

# Economy post - ref: no 
beta_econ <- coefficients(fit_econ_post)["economy_postYes"]
lower_econ <- confint(fit_econ_post)["economy_postYes","2.5 %"]
upper_econ <- confint(fit_econ_post)["economy_postYes","97.5 %"]

# Brief resilience Scale score
beta_resilience <- coefficients(fit_resilience_post)["resilience_scale_post"]
lower_resilience <- confint(fit_resilience_post)["resilience_scale_post","2.5 %"]
upper_resilience <- confint(fit_resilience_post)["resilience_scale_post","97.5 %"]

# Living alone post	 - ref: no 
beta_liv_alone <- coefficients(fit_living_alone_post)["living_alone_postYes"]
lower_liv_alone <- confint(fit_living_alone_post)["living_alone_postYes","2.5 %"]
upper_liv_alone <- confint(fit_living_alone_post)["living_alone_postYes","97.5 %"]

# Neuroticism
beta_neuroticism <- coefficients(fit_neuroticism)["neuroticism"]
lower_neuroticism <- confint(fit_neuroticism)["neuroticism","2.5 %"]
upper_neuroticism <- confint(fit_neuroticism)["neuroticism","97.5 %"]

# Extraversion scale	- ref: no 
beta_extrav <- coefficients(fit_extraversion)["extraversion"]
lower_extrav <- confint(fit_extraversion)["extraversion","2.5 %"]
upper_extrav <- confint(fit_extraversion)["extraversion","97.5 %"]

# Physical activity - Ref: High
# Physical activity - Moderate
beta_physical_mod <- coefficients(fit_physical_post)["physical_postModerate"]
lower_physical_mod <- confint(fit_physical_post)["physical_postModerate","2.5 %"]
upper_physical_mod <- confint(fit_physical_post)["physical_postModerate","97.5 %"]
# Physical activity - Low
beta_physical_low <- coefficients(fit_physical_post)["physical_postLow"]
lower_physical_low <- confint(fit_physical_post)["physical_postLow","2.5 %"]
upper_physical_low <- confint(fit_physical_post)["physical_postLow","97.5 %"]

# # Anxiety - Ref: No
# beta_anxiety <- coefficients(fit_GAD12m_pre)["GAD12m_preYes"]
# lower_anxiety <- confint(fit_GAD12m_pre)["GAD12m_preYes","2.5 %"]
# upper_anxiety <- confint(fit_GAD12m_pre)["GAD12m_preYes","97.5 %"]

# Panic - Ref: No
beta_panic <- coefficients(fit_PAN12m_pre)["PAN12m_preYes"]
lower_panic <- confint(fit_PAN12m_pre)["PAN12m_preYes","2.5 %"]
upper_panic <- confint(fit_PAN12m_pre)["PAN12m_preYes","97.5 %"]

# # Disability pre
beta_disabity_pre <- coefficients(fit_whodas12_pre)["whodas12_pre"]
lower_disabity_pre <- confint(fit_whodas12_pre)["whodas12_pre","2.5 %"]
upper_disabity_pre <- confint(fit_whodas12_pre)["whodas12_pre","97.5 %"]
# # Disability post
beta_disabity_post <- coefficients(fit_whodas12_post)["whodas12_post"]
lower_disabity_post <- confint(fit_whodas12_post)["whodas12_post","2.5 %"]
upper_disabity_post <- confint(fit_whodas12_post)["whodas12_post","97.5 %"]

# # Social support pre
beta_soc_supp_pre <- coefficients(fit_social_support_pre)["social_support_pre_original"]
lower_soc_supp_pre <- confint(fit_social_support_pre)["social_support_pre_original","2.5 %"]
upper_soc_supp_pre <- confint(fit_social_support_pre)["social_support_pre_original","97.5 %"]

# # Social support post
beta_soc_supp_post <- coefficients(fit_social_support_post)["social_support_post_original"]
lower_soc_supp_post <- confint(fit_social_support_post)["social_support_post_original","2.5 %"]
upper_soc_supp_post <- confint(fit_social_support_post)["social_support_post_original","97.5 %"]

# # depression pre
beta_depression_pre <- coefficients(fit_depression_pre)["depression_12m_preYes"]
lower_depression_pre <- confint(fit_depression_pre)["depression_12m_preYes","2.5 %"]
upper_depression_pre <- confint(fit_depression_pre)["depression_12m_preYes","97.5 %"]

# # depression post
beta_depression_post <- coefficients(fit_depression_post)["depression_30d_postYes"]
lower_depression_post <- confint(fit_depression_post)["depression_30d_postYes","2.5 %"]
upper_depression_post <- confint(fit_depression_post)["depression_30d_postYes","97.5 %"]

# Vectors
beta <- c(beta_sex, 
          beta_age,
          beta_age_cat_18_34,
          beta_age_cat_35_49,
          beta_age_cat_65,
          beta_mar_stat_single,
          beta_mar_stat_sep_wid,
          beta_ed_level_less_prim,
          beta_ed_level_prim,
          beta_ed_level_sec,
          beta_solo3_impr,
          beta_solo3_wors,
          beta_econ,
          beta_resilience, 
          beta_liv_alone,
          beta_neuroticism,
          beta_extrav,
          beta_physical_mod,
          beta_physical_low,
          # beta_anxiety,
          beta_panic,
          beta_disabity_pre,
          beta_disabity_post,
          beta_soc_supp_pre,
          beta_soc_supp_post,
          beta_depression_pre,
          beta_depression_post
          ) |> rev()
lower <- c(lower_sex, 
           lower_age,
           lower_age_cat_18_34,
           lower_age_cat_35_49,
           lower_age_cat_65,
           lower_mar_stat_single,
           lower_mar_stat_sep_wid,
           lower_ed_level_less_prim,
           lower_ed_level_prim,
           lower_ed_level_sec,
           lower_solo3_impr,
           lower_solo3_wors,
           lower_econ,
           lower_resilience,
           lower_liv_alone,
           lower_neuroticism,
           lower_extrav,
           lower_physical_mod,
           lower_physical_low,
           # lower_anxiety,
           lower_panic,
           lower_disabity_pre,
           lower_disabity_post,
           lower_soc_supp_pre,
           lower_soc_supp_post,
           lower_depression_pre,
           lower_depression_post
           ) |> rev()
upper <- c(upper_sex, 
           upper_age,
           upper_age_cat_18_34,
           upper_age_cat_35_49,
           upper_age_cat_65,
           upper_mar_stat_single,
           upper_mar_stat_sep_wid,
           upper_ed_level_less_prim,
           upper_ed_level_prim,
           upper_ed_level_sec,
           upper_solo3_impr,
           upper_solo3_wors,
           upper_econ,
           upper_resilience,
           upper_liv_alone,
           upper_neuroticism,
           upper_extrav,
           upper_physical_mod,
           upper_physical_low,
           # upper_anxiety,
           upper_panic,
           upper_disabity_pre,
           upper_disabity_post,
           upper_soc_supp_pre,
           upper_soc_supp_post,
           upper_depression_pre,
           upper_depression_post
           ) |> rev()
study <- c("Sex (Female)", 
           "Age",
           "Age (18-34)",
           "Age (35-49)",
           "Age (>65)",
           "Marital status (Single)",
           "Marital status (Separated/ Widowed)",
           "Education level (Less than primary)",
           "Education level (Primary)",
           "Education level (Secondary)",
           "Social relationships changes (Improved)",
           "Social relationships changes (Worsened)",
           "Economic situation worsened due to COVID-19",
           "Brief Resilience Scale (Post)",
           "Living Alone (Post)",
           "Neuroticism",
           "Extraversion",
           "Physical Activity Post (Moderate)",
           "Physical Activity Post (Low)",
           # "Anxiety",
           "Panic",
           "Disability pre",
           "Disability post",
           "Social support (Pre)",
           "Social support (Post)",
           "Depression 12 months (Pre)",
           "Depression 30 days (Post)"
           ) |> rev()
# df
index <- 1:length(study)
df <- data.frame(study, index, beta, lower, upper)

# plot
ggplot(data=df, aes(y=index, x=beta, xmin=lower, xmax=upper)) +
  geom_point(shape = 18, size = 3, col = "blue") +
  geom_errorbarh(height=.2, col = "blue") +
  scale_y_continuous(breaks=1:nrow(df), labels=df$study) +
  labs(title='Univariate', x='Beta coefficients with 95% CI', y = '') +
  geom_vline(xintercept=0, color='black', linetype='dashed', alpha=.5) +
  theme_minimal()
```

# Multivariate

```{r message=FALSE, warning=FALSE}
fit_multi <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre) #+ 0
    # Fix
    + q1009_sex
    + q1011_age_cat
    + q1012_mar_stat_recat   
    + q1016_highest_recat 
    # random
    + SOLO3
    + economy_post         
    + neuroticism        
    + extraversion        
    + whodas12_pre 
    # + social_support_pre_original
    # + social_support_post_original
    + depression_12m_pre 
    + depression_30d_post 
    ,
    design  = svy_design
  )

# Quick review of significant factors
summary(fit_multi)

# Table
tbl_multi_1 <- 
  fit_multi |> 
  tbl_regression(
    pvalue_fun = purrr::partial(style_sigfig, digits = 3)
  ) |> 
  bold_p(t = 0.05) |>
  add_vif()|> 
  add_global_p(keep = TRUE)
```

## Plot Multivariate

```{r, fig.width= 7, fig.height= 10}
plot_multi <- 
  plot_model(fit_multi, show.values = TRUE, value.offset = .3,
           title = "Change in Loneliness",
           axis.title = "Beta coefficients with 95% CI",
           width = .3,
           group.terms = c(1, 2, 2, 2, 3, 3,  4,  4,  4, 5, 
                           5, 6, 7, 7, 8, 9,  9),
           colors = "Dark2",
           value.size = 5,
           axis.labels = c(
               "Sex (Female)", 
               "Age (18-34)",
               "Age (35-49)",
               "Age (+65)",
               "Marital status (Single)",
               "Marital status (Separated/ Widowed)",
               "Education level (Less than primary)",
               "Education level (Primary)",
               "Education level (Secondary)",
               "Social relationships changes (Improved)",
               "Social relationships changes (Worsened)",
               "Economic situation worsened due to COVID-19",
               "Neuroticism",
               "Extraversion",
               "Disability (Before)",
               # "Social support (Before)",
               # "Social support (During)",
               "Depression 12 months (Before)",
               "Depression 30 days (During)"
           ) |> rev()
           ) +
  font_size(title =20, labels.y = 15, axis_title.x = 15)
```

## Improve the model

```{r}
# How much improve the model if we remove a factor
model1 <- anova(fit_multi, update(fit_multi, .~ . -SOLO3))
model2 <- anova(fit_multi, update(fit_multi, .~ . -economy_post))
model3 <- anova(fit_multi, update(fit_multi, .~ . -neuroticism))
model4 <- anova(fit_multi, update(fit_multi, .~ . -extraversion))
model5 <- anova(fit_multi, update(fit_multi, .~ . -whodas12_pre))
# model6 <- anova(fit_multi, update(fit_multi, .~ . -social_support_pre_original ))
# model7 <- anova(fit_multi, update(fit_multi, .~ . -social_support_post_original ))
model8 <- anova(fit_multi, update(fit_multi, .~ . -depression_12m_pre))
model9 <- anova(fit_multi, update(fit_multi, .~ . -depression_30d_post))


Deleted <- c(model1$test.terms, 
             model2$test.terms,
             model3$test.terms,
             model4$test.terms,
              # model5$test.terms,
              # model6$test.terms,
              model7$test.terms,
              model8$test.terms,
              model9$test.terms)

p <- c(model1$p, 
       model2$p,
       model3$p,
       model4$p,
       model5$p,
       # model6$p,
       # model7$p,
       model8$p,
       model9$p)

Model <- 1:length(Deleted)

data.frame(Model, Deleted, p) |> gt()
```


# Multivariate (interaction sex*age)

```{r}
fit_multi_2 <-
  svyglm(
    formula = loneliness_post ~ offset(loneliness_pre)
    # Fijos
    + q1009_sex
    + q1011_age_cat
    # interaction
    + q1009_sex*q1011_age_cat
    + q1012_mar_stat_recat   
    + q1016_highest_recat    
    # Random
    + SOLO3
    + economy_post         
    + neuroticism        
    + extraversion        
    + whodas12_pre 
    # + social_support_pre_original  
    # + social_support_post_original   
    + depression_12m_pre 
    + depression_30d_post 
    ,
    design  = svy_design
  )

# Quick review of significant factors
summary(fit_multi_2)

# Table
tbl_multi_interaction <- 
  fit_multi_2 |> 
  tbl_regression(
    pvalue_fun = purrr::partial(style_sigfig, digits = 3)
  ) |> 
  bold_p(t = 0.05) |>
  add_vif()|> 
  add_global_p(keep = TRUE)
```

## Plot Multivariate interaction

```{r}
plot_multi_interaction <- 
  plot_model(fit_multi_2, show.values = TRUE, value.offset = .3,
           title = "Change in Loneliness",
           axis.title = "Beta coefficients with 95% CI",
           width = .3,
           group.terms = c(1, 2, 2, 2, 3, 3,  4,  4,  4, 5,
                           5, 6, 7, 7, 8, 9,  9, 10, 10, 10),
           colors = "Dark2",
           value.size = 5,
           axis.labels = c(
               "Sex (Female)",
               "Age (18-34)",
               "Age (35-49)",
               "Age (+65)",
               "Marital status (Single)",
               "Marital status (Separated/ Widowed)",
               "Education level (Less than primary)",
               "Education level (Primary)",
               "Education level (Secondary)",
               "Social relationships changes (Improved)",
               "Social relationships changes (Worsened)",
               "Economic situation worsened due to COVID-19",
               "Neuroticism",
               "Extraversion",
               "Disability (Before)",
               "Depression 12 months (Before)",
               "Depression 30 days (During)", 
               "Sex (Female)*Age (18-34)",
               "Sex (Female)*Age (35-49)",
               "Sex (Female)*Age (+65)"
           ) |> rev()
           ) +
  font_size(title =20, labels.y = 15, axis_title.x = 15)
```

## Compare the models

```{r}
anova(fit_multi, update(fit_multi_2))
```

# To png

## Table 1

```{r}
gt::gtsave(as_gt(tbl), file = "../results_28_jul_22/table_1.png")
```

# Multivariate

## Graphs

### Model 1

```{r}
png("results_28_jul_22/plot_multi_1.png",
    width = 8, height = 10,
    res = 900, units = "in")
plot_multi
dev.off()
```

### Model with interaction


```{r}
png("results_28_jul_22/plot_multi_interaction.png",
    width = 8, height = 12,
    res = 900, units = "in")
plot_multi_interaction
dev.off()
```

## Tables

### Model 1

```{r}
gt::gtsave(as_gt(tbl_multi_1), file = "results_28_jul_22/tbl_multi_1.png")
```

### Model with interaction

```{r}
gt::gtsave(as_gt(tbl_multi_interaction), file = "results_28_jul_22/tbl_multi_interaction.png")
```