---
title: "Graphics Loneliness"
description: "Representation of the central tendency with its confidence intervals"
date: today
author: 
 - name: "Jesus Sierralaya"
   url: https://github.com/JesusSierralaya
   affiliation: CCOMS-UAM
   affiliation-url: https://github.com/CCOMS-UAM
title-block-banner: true
format: 
  html: 
    theme: flatly
    code-fold: true
    code-tools: true
    code-link: true
    toc: true
    number-sections: true
    df-print: paged 
    self-contained: true
link-citations: yes
editor: source
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(lme4)
library(tidyverse)
library(effects)
library(labelled)
library(scales)
library(ggtext)
```

# Load data

```{r}
load(
  here("Cleandata","db_pivot_2.Rda")
)

# Recode
db_pivot_2 <- db_pivot_2 |> 
  to_factor() |> 
  mutate(Assessment =  Assessment |> 
           recode(`Pre-confinement` = "Before",                                              `Post-confinement` = "During"),
         SOLO2 = SOLO2 |> to_factor(),
         material = material |> to_factor(),
         ECON5 = ECON5 |> to_factor()
         )
```

# Mixed Model effect

## Total Fix model

```{r}
Fit_fix <- lmer(Loneliness ~ 0 + Assessment + (1 | ID_ECS), 
                 data = db_pivot_2, 
                 weights = db_pivot_2$wfinal_norm)
```

## Age_cat Mix model 

```{r}
Fit_mix <- lmer(Loneliness ~ 0 + q1011_age_cat * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Sex Mix model 

```{r}
Fit_mix_sex <- lmer(Loneliness ~ 0 + q1009_sex * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Marital status Mix model 

```{r}
Fit_mix_marital <- lmer(Loneliness ~ 0 + q1012_mar_stat_recat * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Education level

```{r}
Fit_mix_edu <- lmer(Loneliness ~ 0 + q1016_highest_recat * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Social relationship

```{r}
Fit_mix_social <- lmer(Loneliness ~ 0 + SOLO3 * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Physical activity post

```{r}
Fit_mix_physical_post <- lmer(Loneliness ~ 0 + physical_post * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Depression pre

```{r}
Fit_mix_depre_pre <- lmer(Loneliness ~ 0 + depression_12m_pre * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Depression post

```{r}
Fit_mix_depre_post <- lmer(Loneliness ~ 0 + depression_30d_post * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Economy post

```{r}
Fit_mix_economy_post <- lmer(Loneliness ~ 0 + economy_post * Assessment + (1 | ID_ECS), 
             data = db_pivot_2, 
             weights = db_pivot_2$wfinal_norm)
```

## Living alone post

```{r}
Fit_mix_liv_alone_post <- lmer(Loneliness ~ 0 + living_alone_post * Assessment + (1 | ID_ECS), 
             data = db_pivot_2, 
             weights = db_pivot_2$wfinal_norm)
```

## Virtual contact

```{r}
Fit_mix_SOLO2 <- lmer(Loneliness ~ 0 + SOLO2 * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Material deprivation
```{r}
Fit_mix_material <- lmer(Loneliness ~ 0 + material * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Unemployment (ECON5)

```{r}
Fit_mix_ECON5 <- lmer(Loneliness ~ 0 + ECON5 * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Physical activity 

```{r}
Fit_mix_physical_pre <- lmer(Loneliness ~ 0 + physical_pre * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```


## Health status pre

```{r}
Fit_mix_health_pre <- lmer(Loneliness ~ 0 + health_pre * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Cantril striving (q7008d_cantril) pre

```{r}
Fit_mix_cantril_pre <- lmer(Loneliness ~ 0 + q7008d_cantril * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Neuroticism

```{r}
Fit_mix_neuroticism <- lmer(Loneliness ~ 0 + neuroticism * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```

## Social support pre puntuacion original 

```{r}
Fit_mix_soc_sup_pre_original <- 
   lmer(Loneliness ~ 0 + social_support_pre_original * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```


## Social support POST puntuacion original 

```{r}
Fit_mix_soc_sup_post_original <- 
   lmer(Loneliness ~ 0 + social_support_post_original * Assessment + (1 | ID_ECS), 
             data = db_pivot_2,
             weights = db_pivot_2$wfinal_norm)
```


# Graphics

## Parameters

```{r}
lim_inf <- 3.1
lim_sup <- 6.5
# Legend 
leg_dist <- 0
theme_set(theme_minimal())
```


## Total

```{r}
# Effects
effects_total <- effect("Assessment", Fit_fix) |> as.data.frame() |> 
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_total <- effects_total |>
  ggplot(aes(x = Assessment, y = fit)) + 
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf, lim_sup))
plot_total
```


```{r}
# Effects
effects_total <- effect("Assessment", Fit_fix) |> as.data.frame() |> 
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_total <- effects_total |>
  ggplot(aes(x = Assessment, y = fit)) + 
  geom_point(size = 5)  + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .2, size = 1.5) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40)) #+
  # coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", 
  #                              title.hjust = .5, nrow = 2)) +
  # labs(color = "**Total**")  
# plot_total

# Graph slopes
    # geom_line(size = .5, position = position_dodge(.5),
    #         linetype = "dotted")
plot_total_slope <- effects_total |>
  ggplot(aes(x = Assessment, y = fit, group = 1)) + 
  geom_line(size = 1) +
  geom_point(size = 5)  + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .2, size = 1.5) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40)) 
```

## Age

```{r}
# Effects
effects_age_cat <- effect("q1011_age_cat:Assessment", Fit_mix) |> as.data.frame() |>
            mutate(Assessment =  Assessment |> relevel("Before"),
           q1011_age_cat = q1011_age_cat |> fct_relevel("18-34", "35-49", "50-64"))
                                  
# Graph
plot_age <- effects_age_cat |> ggplot(aes(x = Assessment, y = fit, 
                   group = q1011_age_cat, color = q1011_age_cat)) + 
   # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  guides(colour = guide_legend(title.position = "top", 
                               title.hjust = .5, nrow = 2)) +
  labs(color = "**Age grouped**")  +
  scale_color_brewer(palette = "Dark2")
plot_age
```


```{r}
# Effects
effects_age_cat <- effect("q1011_age_cat:Assessment", Fit_mix) |> as.data.frame() |>
            mutate(Assessment =  Assessment |> relevel("Before"),
           q1011_age_cat = q1011_age_cat |> fct_relevel("18-34", "35-49", "50-64"))
                                  
# Graph
plot_age <- effects_age_cat |> ggplot(aes(x = Assessment, y = fit, 
                   group = q1011_age_cat, color = q1011_age_cat)) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5) + 
  theme(#legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
         legend.key.height = unit(1, "in")
        #legend.margin = margin(t = leg_dist)
        # legend.box.margin = margin(-20, -20, -20, -20)
        ) + 
  # coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", 
                               # title.hjust = .5, 
                             # nrow = 4)) +
  labs(color = "")
# plot_age

# Graph slopes   ------------
plot_age_slope <- 
  effects_age_cat |> ggplot(aes(x = Assessment, y = fit, 
                   group = q1011_age_cat, color = q1011_age_cat)) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5,
                alpha = .2) + 
  geom_line(size = 1.5, position = position_dodge(.5)) +
  theme(#legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")) + 
  labs(color = "")

```

## Sex

```{r}
# Effects
effects_sex <- effect("q1009_sex:Assessment", Fit_mix_sex) |> as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_sex <- effects_sex |> 
  ggplot(aes(x = Assessment, y = fit, group = q1009_sex, color = q1009_sex)) + 
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  guides(colour = guide_legend(title.position = "top", title.hjust = .5, nrow = 2)) +
  labs(color = "**Sex**")
plot_sex
```

## Marital Status


```{r}
# Effects  ------
effects_marital <- 
  effect("q1012_mar_stat_recat:Assessment", Fit_mix_marital) |> 
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"),
           q1012_mar_stat_recat = q1012_mar_stat_recat |> fct_relevel("Single"))

# Graph  -------
plot_marital <- effects_marital |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = q1012_mar_stat_recat, 
             color = str_wrap(q1012_mar_stat_recat, 15))) + 
    geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  guides(colour = guide_legend(title.position = "top", title.hjust = .5, nrow = 2)) +
  labs(color = "**Marital status**")
plot_marital

```

```{r}
# Effects  ------
effects_marital <- 
  effect("q1012_mar_stat_recat:Assessment", Fit_mix_marital) |> 
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"),
           q1012_mar_stat_recat = q1012_mar_stat_recat |> fct_relevel("Single"))

# Graph  -------
plot_marital <- effects_marital |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = q1012_mar_stat_recat, 
             color = str_wrap(q1012_mar_stat_recat, 15))) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5)  + 
  theme(#legend.position = "top",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        # legend.margin = margin(t = leg_dist)
        ) +
  # coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", title.hjust = .5, nrow = 3)) +
  labs(color = "")
# plot_marital

# Graph slopes   ------------
plot_marital_slope <- effects_marital |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = q1012_mar_stat_recat, 
             color = str_wrap(q1012_mar_stat_recat, 15))) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5, alpha = .2) + 
  geom_line(size = 1.5, position = position_dodge(.5)) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) +
  labs(color = "")
```

## Education level

```{r}
# Effects
effects_ed <- 
  effect("q1016_highest_recat:Assessment", Fit_mix_edu) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_ed <- effects_ed |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = q1016_highest_recat, 
             color = q1016_highest_recat)) + 
    geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  guides(colour = guide_legend(title.position = "top", title.hjust = .5, nrow = 2)) +
  labs(color = "**Education level**")
plot_ed
```


```{r}
# Effects
effects_ed <- 
  effect("q1016_highest_recat:Assessment", Fit_mix_edu) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_ed <- effects_ed |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = q1016_highest_recat, 
             color = q1016_highest_recat)) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + labs(color = "")
# plot_ed

# Graph slopes   ------------
plot_ed_slope <- effects_ed |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = q1016_highest_recat, 
             color = q1016_highest_recat)) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5, alpha = .2) + 
  geom_line(size = 1.5, position = position_dodge(.5)) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + labs(color = "")
```


## Social relationship

```{r}
# Effects
effects_social <- 
  effect("SOLO3:Assessment", Fit_mix_social) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_social <- effects_social |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = SOLO3, color = SOLO3)) + 
    geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  guides(colour = guide_legend(title.position = "top", title.hjust = .5, nrow = 2)) +
  labs(color = "**Social relationship**")
plot_social
```


```{r}
# Effects
effects_social <- 
  effect("SOLO3:Assessment", Fit_mix_social) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_social <- effects_social |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = SOLO3, color = SOLO3)) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + 
  labs(color = "")
# plot_social

# Graph slope ----
plot_social_slope <- 
  effects_social |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = SOLO3, color = SOLO3)) + 
  geom_point(position = position_dodge(.5),
             size = 5, aes(alpha = SOLO3)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5, alpha = .2) + 
  geom_line(size = 1.5, position = position_dodge(.5),
            aes(alpha = SOLO3)) +
  scale_alpha_manual(values = c(.2, 1, .2), guide = "none") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + 
  labs(color = "")
```


## Physical activity post

```{r}
# # Effects
# effects_physical_post <- 
#   effect("physical_post:Assessment", Fit_mix_physical_post) |> # Change Here [2]
#   as.data.frame() |>
#     mutate(Assessment =  Assessment |> recode_factor(`Pre-confinement` = "Pre",
#                                               `Post-confinement` = "Post",
#                                               .ordered = TRUE))
# # Graph
# plot_phys_post <- effects_physical_post |> 
#   ggplot(aes(x = Assessment, y = fit, 
#              group = physical_post, color = physical_post)) + # Change Here [2]
#   # This stay the same
#   geom_point(position = position_dodge(.5)) + 
#   geom_errorbar(aes(ymin = lower, ymax = upper), 
#                 position = position_dodge(.5), width = .2) + 
#   theme(legend.position = "top",
#         legend.title = element_markdown(),
#         axis.title.x = element_blank(),
#         axis.title.y = element_blank()) + 
#   coord_cartesian(ylim = c(lim_inf, lim_sup)) +
#   guides(colour = guide_legend(title.position = "top", 
#                                title.hjust = .5, nrow = 3)) +
#   labs(color = "**Physical activity**")
# plot_phys_post
```

## Depression pre

```{r}
# Effects
effects_depre_pre <- # Change name effects_var
  effect("depression_12m_pre:Assessment", Fit_mix_depre_pre) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_depre_pre <- 
  effects_depre_pre |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = depression_12m_pre, color = depression_12m_pre)) + 
    geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  guides(colour = guide_legend(title.position = "top", title.hjust = .5, nrow = 2)) +
  labs(color = "**Depression Before**")
plot_depre_pre
```

```{r}
# Effects
effects_depre_pre <- # Change name effects_var
  effect("depression_12m_pre:Assessment", Fit_mix_depre_pre) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_depre_pre <- 
  effects_depre_pre |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = depression_12m_pre, color = depression_12m_pre)) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + 
  labs(color = "")
# plot_depre_pre

# Graph slope ----
plot_depre_pre_slope <- 
  effects_depre_pre |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = depression_12m_pre, 
             color = depression_12m_pre)) + 
  geom_point(position = position_dodge(.5),
             size = 5, aes(alpha = depression_12m_pre)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5, alpha = .2) + 
  geom_line(size = 1.5, position = position_dodge(.5),
            aes(alpha = depression_12m_pre)) +
  scale_alpha_manual(values = c(.2, 1), guide = "none") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + 
  labs(color = "")
```

## Depression post


```{r}
# Effects
effects_depre_post <- # Change name effects_var
  effect("depression_30d_post:Assessment", Fit_mix_depre_post) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))


# Graph
plot_depre_post <- effects_depre_post |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = depression_30d_post, 
             color = depression_30d_post)) + 
    geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf,lim_sup)) +
  guides(colour = guide_legend(title.position = "top", title.hjust = .5, nrow = 2)) +
  labs(color = "**Depression During**")
plot_depre_post
```


```{r}
# Effects
effects_depre_post <- # Change name effects_var
  effect("depression_30d_post:Assessment", Fit_mix_depre_post) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))


# Graph
plot_depre_post <- effects_depre_post |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = depression_30d_post, 
             color = depression_30d_post)) + 
  geom_point(position = position_dodge(.5),
             size = 5) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + 
  labs(color = "")
# plot_depre_post

# slope ----
plot_depre_post_slope <- 
  effects_depre_post |> 
  ggplot(aes(x = Assessment, y = fit, 
             group = depression_30d_post, 
             color = depression_30d_post)) + 
  geom_point(position = position_dodge(.5),
             size = 5, aes(alpha = depression_30d_post)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2,
                size = 1.5, alpha = .2) + 
  geom_line(size = 1.5, position = position_dodge(.5),
            aes(alpha = depression_30d_post)) +
  scale_alpha_manual(values = c(.2, 1), guide = "none") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 40),
        legend.key.height = unit(1, "in")
        ) + 
  labs(color = "")
```

## Economy post

```{r}
# # Effects
# effects_econ_post <- # Change name effects_var
#   effect("economy_post:Assessment", Fit_mix_economy_post) |> # Change Here [2]
#   as.data.frame() |>
#     mutate(Assessment =  Assessment |> recode_factor(`Pre-confinement` = "Pre",
#                                               `Post-confinement` = "Post",
#                                               .ordered = TRUE))
# # Graph
# plot_econ_post <- effects_econ_post |> # Copy name effects
#   ggplot(aes(x = Assessment, y = fit, 
#              group = economy_post, color = economy_post)) + # Change Here [2]
#   # This stay the same
#   geom_point(position = position_dodge(.5)) + 
#   geom_errorbar(aes(ymin = lower, ymax = upper), 
#                 position = position_dodge(.5), width = .2) + 
#   theme(legend.position = "top",
#         legend.title = element_markdown(),
#         axis.title.x = element_blank(),
#         axis.title.y = element_blank()) + 
#   coord_cartesian(ylim = c(lim_inf, lim_sup)) +
#   guides(colour = guide_legend(title.position = "top", 
#                                title.hjust = .5, nrow = 2)) +
#   labs(color = "**Economy worsened (Post)**") 
# plot_econ_post
```

## Living alone 

```{r}
# Effects
effects_liv_alone_post <- # Change name effects_var
  effect("living_alone_post:Assessment", Fit_mix_liv_alone_post) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_liv_alone_post <- effects_liv_alone_post |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = living_alone_post, color = living_alone_post)) + # Change Here [2]
  # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  guides(colour = guide_legend(title.position = "top", 
                               title.hjust = .5, nrow = 2)) +
  labs(color = "**Living alone (Post)**")  

plot_liv_alone_post
```

## Virtual contact 

```{r}
# Effects
effects_SOLO2 <- # Change name effects_var
  effect("SOLO2:Assessment", Fit_mix_SOLO2) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"), 
             SOLO2 = SOLO2 |> recode_factor(`1` = "Daily",
                                      `2` = "Once a week", 
                                      `3` = "Less than once a week",
                                      `4` = "Never", 
                                      .ordered = TRUE))

# Graph
plot_SOLO2 <- effects_SOLO2 |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = SOLO2, color = SOLO2)) + # Change Here [2]
  # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  guides(colour = guide_legend(title.position = "top", 
                               title.hjust = .5, nrow = 2)) +
  labs(color = "**Virtual contact (SOLO2)**")  

plot_SOLO2
```

## Material deprivation

```{r}
# Effects
effects_material <- # Change name effects_var
  effect("material:Assessment", Fit_mix_material) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_material <- effects_material |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = material, color = material)) + # Change Here [2]
  # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  guides(colour = guide_legend(title.position = "top", 
                               title.hjust = .5, nrow = 2)) +
  labs(color = "**Material deprivation**") 
plot_material
```


## Unemployment (ECON5)

```{r}
effects_ECON5 <- # Change name effects_var
  effect("ECON5:Assessment", Fit_mix_ECON5) |> # Change Here [2]
  as.data.frame() |>
  mutate(Assessment =  Assessment |> relevel("Before"), 
             ECON5 = ECON5 |> recode_factor(`1` = "Yes",
                                      `2` = "No",
                                      .ordered = TRUE))

# Graph
plot_ECON5 <- effects_ECON5 |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = ECON5, color = ECON5)) + # Change Here [2]
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  guides(colour = guide_legend(title.position = "top", 
                               title.hjust = .5, nrow = 2)) +
  labs(color = "**Unemployment (ECON5)**")  +
  scale_color_brewer(palette = "Dark2")

plot_ECON5
```

## Physical activity pre

Fit_mix_physical_pre

```{r}
# Effects
effects_physical_pre <- # Change name effects_var
  effect("physical_pre:Assessment", Fit_mix_physical_pre) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_physical_pre <- effects_physical_pre |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = physical_pre, color = physical_pre)) + # Change Here [2]
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  theme(legend.position = "top",
        legend.title = element_markdown(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.margin = margin(t = leg_dist)
        ) + 
  coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  guides(colour = guide_legend(title.position = "top", 
                               title.hjust = .5, nrow = 2)) +
  labs(color = "**Physical activity (Before)**")  +
  scale_color_brewer(palette = "Dark2")
plot_physical_pre
```


## Health status pre


health_pre

```{r}
# Effects
effects_health_pre <- # Change name effects_var
  effect("health_pre:Assessment", Fit_mix_health_pre) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_health_pre <- effects_health_pre |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = health_pre, color = health_pre)) + # Change Here [2]
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  # theme(legend.position = "top",
  #       legend.title = element_markdown(),
  #       axis.title.x = element_blank(),
  #       axis.title.y = element_blank(),
  #       legend.margin = margin(t = leg_dist)
  #       ) + 
  # coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", 
  #                              title.hjust = .5, nrow = 2)) +
  labs(color = "**Health status (Before)**")  #+
  # scale_color_brewer(palette = "Dark2")
plot_health_pre

```

## Cantril striving (q7008d_cantril) pre

```{r}
# Effects
effects_cantril_pre <- # Change name effects_var
  effect("q7008d_cantril:Assessment", Fit_mix_cantril_pre) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_cantril_pre <- effects_cantril_pre |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = q7008d_cantril, color = q7008d_cantril)) + # Change Here [2]
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  # theme(legend.position = "top",
  #       legend.title = element_markdown(),
  #       axis.title.x = element_blank(),
  #       axis.title.y = element_blank(),
  #       legend.margin = margin(t = leg_dist)
  #       ) + 
  # coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", 
  #                              title.hjust = .5, nrow = 2)) +
  labs(color = "**Cantril Self-Anchoring Striving Scale (Before)**")  #+
  # scale_color_brewer(palette = "Dark2")
plot_cantril_pre
```


## Neuroticism

Fit_mix_neuroticism 

```{r}
# Effects
effects_neuroticism <- # Change name effects_var
  effect("neuroticism:Assessment", Fit_mix_neuroticism) |> # Change Here [2]
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_neuroticism <- effects_neuroticism |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = neuroticism, color = neuroticism)) + # Change Here [2]
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  # theme(legend.position = "top",
  #       legend.title = element_markdown(),
  #       axis.title.x = element_blank(),
  #       axis.title.y = element_blank(),
  #       legend.margin = margin(t = leg_dist)
  #       ) + 
  # coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", 
  #                              title.hjust = .5, nrow = 2)) +
  labs(color = "**Neuroticism**")  #+
  # scale_color_brewer(palette = "Dark2")
plot_neuroticism
```

## Social support pre puntuacion original 

```{r}
# Effects
effects_soc_sup_pre_original <- # Change name effects_var
  effect("social_support_pre_original:Assessment", Fit_mix_soc_sup_pre_original) |> # Change Here 2
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_soc_sup_pre_original <- effects_soc_sup_pre_original |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = social_support_pre_original,
             color = social_support_pre_original)) + # Change Here [2]
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  # theme(legend.position = "top",
  #       legend.title = element_markdown(),
  #       axis.title.x = element_blank(),
  #       axis.title.y = element_blank(),
  #       legend.margin = margin(t = leg_dist)
  #       ) + 
  # coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", 
  #                              title.hjust = .5, nrow = 2)) +
  labs(color = "**Social Support pre original scale**")  #+
  # scale_color_brewer(palette = "Dark2")

plot_soc_sup_pre_original
```

## Social support POST puntuacion original 

```{r}
# Effects
effects_soc_sup_post_original <- # Change name effects_var
  effect("social_support_post_original:Assessment", Fit_mix_soc_sup_post_original) |> # Change Here
  as.data.frame() |>
      mutate(Assessment =  Assessment |> relevel("Before"))

# Graph
plot_soc_sup_post_original <- effects_soc_sup_post_original |> # Copy name effects
  ggplot(aes(x = Assessment, y = fit, 
             group = social_support_post_original,
             color = social_support_post_original)) + # Change Here [2]
 # This stay the same
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(.5), width = .2) + 
  # theme(legend.position = "top",
  #       legend.title = element_markdown(),
  #       axis.title.x = element_blank(),
  #       axis.title.y = element_blank(),
  #       legend.margin = margin(t = leg_dist)
  #       ) + 
  # coord_cartesian(ylim = c(lim_inf, lim_sup)) +
  # guides(colour = guide_legend(title.position = "top", 
  #                              title.hjust = .5, nrow = 2)) +
  labs(color = "**Social Support POST original scale**")  #+
  # scale_color_brewer(palette = "Dark2")

plot_soc_sup_post_original
```

<!-- # Merge plots -->

<!-- With `cowplot` package -->

<!-- ```{r} -->
<!-- #| fig-width: 7 -->
<!-- #| fig-height: 12 -->
<!-- library(cowplot) -->
<!-- # library(ggExtra) # + removeGridY() -->
<!-- # library(ggthemes)  -->
<!-- theme_set(theme_minimal()) -->
<!-- plot_grid( -->
<!--   plot_age, plot_sex, plot_marital,  -->
<!--   plot_ed, plot_social, -->
<!--   plot_depre_pre, plot_depre_post, -->
<!--   plot_liv_alone_post,  -->
<!--   ncol = 3, nrow = 4, -->
<!--   align = 'hv' -->
<!-- )  -->
<!-- ``` -->

<!-- # To png -->

<!-- ## Total -->
<!-- ```{r} -->
<!-- png(file = "../Presentation_1/plot_total.png", -->
<!--     width = 10, height = 6, -->
<!--     res = 900, units = "in") -->
<!-- plot_total -->
<!-- dev.off() -->
<!-- # slope -->
<!-- png(file = "../Presentation_1/plot_total_slope.png", -->
<!--     width = 10, height = 6, -->
<!--     res = 900, units = "in") -->
<!-- plot_total_slope -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Age -->

<!-- ```{r} -->
<!-- png(file = "../Presentation_1/plot_age.png",  -->
<!--     width = 15, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_age -->
<!-- dev.off() -->
<!-- # slope -->
<!-- png(file = "../Presentation_1/plot_age_slope.png",  -->
<!--     width = 15, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_age_slope -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Marital status -->

<!-- ```{r} -->
<!-- png(file = "../Presentation_1/plot_marital.png",  -->
<!--     width = 15, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_marital -->
<!-- dev.off() -->
<!-- # slope -->
<!-- png(file = "../Presentation_1/plot_marital_slope.png",  -->
<!--     width = 15, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_marital_slope -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Education level -->

<!-- ```{r} -->
<!-- png(file = "../Presentation_1/plot_ed.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_ed -->
<!-- dev.off() -->
<!-- # slope -->
<!-- png(file = "../Presentation_1/plot_ed_slope.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_ed_slope -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Social relationship -->

<!-- ```{r} -->
<!-- png(file = "../Presentation_1/plot_social.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_social -->
<!-- dev.off() -->
<!-- # slope -->
<!-- png(file = "../Presentation_1/plot_social_slope.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_social_slope -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Depresssion pre -->

<!-- ```{r} -->
<!-- png(file = "../Presentation_1/plot_depre_pre.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_depre_pre -->
<!-- dev.off() -->
<!-- # slope -->
<!-- png(file = "../Presentation_1/plot_depre_pre_slope.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_depre_pre_slope -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Depresssion post -->

<!-- ```{r} -->
<!-- png(file = "../Presentation_1/plot_depre_post.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_depre_post -->
<!-- dev.off() -->
<!-- # slope -->
<!-- png(file = "../Presentation_1/plot_depre_post_slope.png",  -->
<!--     width = 17, height = 9, -->
<!--     res = 900, units = "in") -->
<!-- plot_depre_post_slope -->
<!-- dev.off() -->
<!-- ``` -->