---
title: "Brief summary of the analyses on the changes in loneliness during the first wave in Spain"
author: 
 - name: "Jesus Sierralaya"
   url: https://github.com/JesusSierralaya
   affiliation: CCOMS-UAM
   affiliation-url: https://github.com/CCOMS-UAM
date: today
# format: 
#   revealjs:
#     # footer: "Changes in loneliness during the first wave in Spain"
#     slide-number: true
#     transition: slide
#     embed-resources: true
format:
  revealjs: 
    preview-links: auto
    css: styles.css
    footer: <https://www.ccomsuam.org>
    slide-number: true
---

### Loneliness

-   Quality and quantity of relationships desired

-   Sustained loneliness results in depression, sleep disturbances, cognitive decline, cardiovascular disease and risk-taking behaviors

### Loneliness in lockdown

-   Social restrain due to COVID-19

-   Is there a change in loneliness?

-   Other studies have different results but those do not have pandemic information (ad hoc questions)

------------------------------------------------------------------------

### Difference in loneliness by group

-   **Risk factors**: younger age, being woman, unemployment, financial concerns, pre-existing mental disorders, low sleep quality

-   **Protective factors**: being married or in partnership, living with others, or a greater social support

### Aims

-   **Explore factors** related with changes in loneliness

-   Estimate a **multivariate model** that explain this change

# Method

## Sample

-   Project: Edad con Salud

-   n = 1002; 18+ from regions of Madrid and Barcelona

-   Baseline: From June 17, 2019 to May 14, 2020

-   Follow-up: From May 21, 2020 to Jun 20, 2020

\[draw time-line\]

## Measurements

-   **Loneliness** UCLA (Pancho et al, 2020)

### Sociodemographic covariates

-   Age

-   Sex

-   Marital status

-   Education level

### Ad hoc COVID-questions

-   Social relationship change

-   Worsening in economy

-   Living alone

## Validated scales

-   **Resilience** (Rodríguez-Rey et al., 2016)

-   **Eysenck's personality traits** (Sandín et al., 2002)

-   **Physical activity** (Armstrong y Bull, 2006)

-   **Disability** (Luciano et al., 2010)

-   **Anxiety** (Kessler & Üstun, 2004)

-   **Panic** (Kessler & Üstun, 2004)

-   **Depression** (Kessler & Üstun, 2004).

# Results

## Loneliness total

<!-- Import and clean data -->

```{r}
#| file: ../../throughput/import_clean.R
#| warning: false
```

<!-- Graphs -->

```{r}
#| file: ../../throughput/graphs.R
#| warning: false
#| message: false
```

```{r}
plot_total + theme(text = element_text(size = 20))
```

